On Sample Size for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-05-31 Manuscript/manuscript.tex
fixed missing curly braces for figure references

As shown in Figure~\ref{fig:phi}, Percentile CIs appear to suffer from bias; specifically, they seem to heavily underestimate $\phi$. As shown in Figure~\ref{fig:bc, $BC$ CIs do seem to correct this bias on average, but the width of the 
CIs is very inconsistent. From Figure~\ref{fig:prop, we can see that 
$prop$ CIs correct the bias using $\hat{bias} = \bar\theta_n^{(b)} - \hat\theta_n$, which seems to usually be negative, indicating a positive correction from
interval construction in \ref{sec:bbci}.

>>>>

As shown in Figure~\ref{fig:phi}, Percentile CIs appear to suffer from bias; specifically, they seem to heavily underestimate $\phi$. As shown in Figure~\ref{fig:bc}, $BC$ CIs do seem to correct this bias on average, but the width of the 
CIs is very inconsistent. From Figure~\ref{fig:prop}, we can see that 
$prop$ CIs correct the bias using $\hat{bias} = \bar\theta_n^{(b)} - \hat\theta_n$, which seems to usually be negative, indicating a positive correction from
interval construction in Section~\ref{sec:bbci}.
